---
title: "Publications"
format:
  html:
    self-contained: true
    toc: true
    toc-location: right
    toc-expand: 1
    toc-depth: 3
---

```{=html}
<style>
/* ─── METRICS ──────────────────────────────────────────── */
.metrics-grid {
  display: grid;
  grid-template-columns: 210px 1fr;
  gap: 2rem;
  align-items: center;
  margin-bottom: 2.5rem;
}
.scholar-badge { margin-bottom: 1rem; }
.stat-cards { display: flex; flex-direction: column; gap: 0.6rem; }
.stat-card {
  display: flex;
  align-items: center;
  gap: 0.85rem;
  background: #f8faff;
  border: 1px solid #dce8fb;
  border-left: 4px solid #1a73e8;
  border-radius: 10px;
  padding: 0.65rem 1rem;
}
.stat-icon { font-size: 1.35rem; flex-shrink: 0; }
.stat-label { font-size: 0.7rem; text-transform: uppercase; letter-spacing: 0.06em; color: #6b7280; margin: 0; }
.stat-value { font-size: 1.45rem; font-weight: 700; color: #1a73e8; margin: 0; line-height: 1.1; }

/* ─── PUBLICATION CARDS ─────────────────────────────────── */
.pub-section ul { list-style: none; padding-left: 0; }
.pub-section li {
  background: #fff;
  border: 1px solid #e5e7eb;
  border-left: 4px solid #1a73e8;
  border-radius: 10px;
  padding: 0.9rem 1.2rem;
  margin: 0.55rem 0;
  box-shadow: 0 1px 3px rgba(0,0,0,0.05);
  transition: box-shadow 0.2s ease, transform 0.2s ease;
}
.pub-section li:hover {
  box-shadow: 0 4px 16px rgba(26,115,232,0.15);
  transform: translateX(5px);
}
/* Year pill badges */
.pub-section h4 {
  background: #1a73e8;
  color: #fff !important;
  font-size: 0.85rem;
  font-weight: 600;
  padding: 0.22rem 0.9rem;
  border-radius: 999px;
  margin-top: 1.8rem;
  margin-bottom: 0.7rem;
  width: fit-content;
}
.pub-section h4 .anchor { display: none !important; }
.pub-section h4 a { color: #fff !important; text-decoration: none; }

/* ─── R PACKAGES ─────────────────────────────────────────── */
.pkg-section ul { list-style: none; padding-left: 0; }
.pkg-section li {
  background: #faf8ff;
  border: 1px solid #e0dbfb;
  border-left: 4px solid #6366f1;
  border-radius: 10px;
  padding: 0.9rem 1.2rem;
  margin: 0.55rem 0;
  box-shadow: 0 1px 3px rgba(0,0,0,0.04);
  transition: box-shadow 0.2s ease, transform 0.2s ease;
}
.pkg-section li:hover {
  box-shadow: 0 4px 16px rgba(99,102,241,0.15);
  transform: translateX(5px);
}

/* ─── TALKS & POSTERS ────────────────────────────────────── */
.conf-section ul { list-style: none; padding-left: 0; }
.conf-section li {
  background: #f9fffe;
  border: 1px solid #d0f0e8;
  border-left: 4px solid #10b981;
  border-radius: 10px;
  padding: 0.9rem 1.2rem;
  margin: 0.55rem 0;
  box-shadow: 0 1px 3px rgba(0,0,0,0.04);
  transition: box-shadow 0.2s ease, transform 0.2s ease;
}
.conf-section li:hover {
  box-shadow: 0 4px 16px rgba(16,185,129,0.15);
  transform: translateX(5px);
}

hr { border: none; border-top: 1px solid #e5e7eb; margin: 2rem 0; }
</style>
```

```{r import_scholar, echo=FALSE}
library("scholar")
id <- "p-N6-8YAAAAJ"
x <- get_profile(id)
citations <- get_citation_history(id)
```

<div class="metrics-grid">
<div>
<div class="scholar-badge">

[![](https://img.shields.io/badge/Google%20Scholar-Profile-blue?logo=google-scholar&logoColor=white)](https://scholar.google.com/citations?user=p-N6-8YAAAAJ)

</div>
<div class="stat-cards">
<div class="stat-card">
<span class="stat-icon">📚</span>
<div><div class="stat-label">Total Citations</div><div class="stat-value">`r x$total_cites`</div></div>
</div>
<div class="stat-card">
<span class="stat-icon">🧠</span>
<div><div class="stat-label">h-index</div><div class="stat-value">`r x$h_index`</div></div>
</div>
<div class="stat-card">
<span class="stat-icon">🏆</span>
<div><div class="stat-label">i10-index</div><div class="stat-value">`r x$i10_index`</div></div>
</div>
</div>
</div>
<div>

```{r plot_citations, echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
plot_ly(
  data = citations,
  x = ~year,
  y = ~cites,
  type = 'bar',
  marker = list(color = '#1a73e8'),
  hoverinfo = 'text',
  text = ~paste("Year:", year, "<br>Citations:", cites)
) %>%
  layout(
    xaxis = list(
      tickmode = "array",
      tickvals = citations$year,
      ticktext = citations$year,
      tickangle = -45
    ),
    yaxis = list(title = "Citations"),
    margin = list(b = 80)
  )
```

</div>
</div>

::: pub-section

### Scientific papers

#### 2025

-   *A systematic benchmark of integrative strategies for microbiome-metabolome data*\
    L. Mangnier$^\star$, [**A. Bodein**]{.underline}$^\star$, M. Mariaz, A. Mathieu, M.P. Scott-Boyer, N. Vashist, M.S. Bramble, A. Droit <br>\
    Communications Biology, <https://doi.org/10.1038/s42003-025-08515-9>

-   *Improving drug repositioning with negative data labeling using large language models*\
    M. Picard, M. Leclercq, [**A. Bodein**]{.underline}, M.P. Scott-Boyer, O. Perin, A. Droit <br> Journal of Cheminformatics, <https://doi.org/10.1186/s13321-025-00962-0>

#### 2024

-   *Target repositioning using multi-layer networks and machine learning: the case of prostate cancer*\
    M. Picard, M.P. Scott-Boyer, [**A. Bodein**]{.underline}, M. Leclercq, J. Prunier, O. Perin, A. Droit <br> Computational and Structural Biotechnology Journal, <https://doi.org/10.1016/j.csbj.2024.06.012>

-   *Combined transcriptomics and proteomics unveil the impact of vitamin C in modulating specific protein abundance in the mouse liver*\
    Aumailley, L., Bodein A., Adjibade, P. et al. <br> BMC Biological Research, <https://doi.org/10.1186/s40659-024-00509-x>

-   *Proteomic Profiling of Samples Derived from a Murine Model Following Cryptococcus neoformans Infection*\
    Muselius B., [**A. Bodein**]{.underline}, Roux-Dalvai F., Droit A., Geddes-McAlister J. <br> Methods in Molecular Biology (Book chapter), <https://doi.org/10.1007/978-1-0716-3722-7_9>

-   *SOS genes are rapidly induced while translesion synthesis polymerase activity is temporally regulated*\
    O. E. T. Bergum, A. H. Singleton, L. M. Røst, [**A. Bodein**]{.underline}, M.-P. Scott-Boyer, M. B. Rye, A. Droit, P. Bruheim, M. Otterlei <br> Frontiers in Microbiology, <https://doi.org/10.3389/fmicb.2024.1373344>

#### 2023

-   *Multi-Omics Data Integration Reveals Key Variables Contributing to Subgingival Microbiome Dysbiosis-Induced Inflammatory Response in a Hyperglycemic Microenvironment*\
    S. Lafleur$^\star$, [**A. Bodein**]{.underline}$^\star$, J. M. M. Mutombo, A. Mathieu, C. Joly Beauparlant, X. Minne, F. Chandad, A. Droit, V. P. Houde <br>\
    International Journal of Molecular Sciences, <https://doi.org/10.3390/ijms24108832>

-   *High dairy products intake modifies the correlation between α-tocopherol levels and serum proteins related to lipid metabolism in subjects at risk of type 2 diabetes*\
    A. Mahdavi, M. Leclercq, [**A. Bodein**]{.underline}, C. Gotti, K. Greffard, J.F. Bilodeau, A. Droit, M. Lebel, I. Rudkowska <br> Journal of Functional Foods, <https://doi.org/10.1016/j.jff.2022.105375>

-   *Decoding Epidermis Reconstruction through Time-course Multi-omics Data Integration*\
    E. Bou Samra, C. Tacheau, M.P. Scott-Boyer, [**A. Bodein**]{.underline}, A. Foucher, K. Abed, V. Segaud, F. Thillou, N. Boyera, N. Misra, A. Droit, O. Perin, N. Cavusoglu <br> IFSCC Magazine, Volume 25(5), Winner of the Basic Research Award

#### 2022

-   *Overview of methods for characterization and visualization of a protein-protein interaction network in a multi-omics integration context*\
    V. Robin, [**A. Bodein**]{.underline}, M.P. Scott-Boyer, M. Leclercq, O. Perin, A. Droit <br> Frontiers in Molecular Biosciences, <https://doi.org/10.3389/fmolb.2022.962799>

-   *The interaction of secreted phospholipase A2-IIA with the microbiota alters its lipidome and promotes inflammation*\
    E. Doré, C. Joly-Beauparlant, S. Morozumi, A. Mathieu, T. Lévesque, I. Allaeys, AC. Duchez, N. Cloutier, M. Leclercq, [**A. Bodein**]{.underline}, C. Payré, C. Martin, A. Petit-Paitel, M. H. Gelb, M. Rangachari, M. Murakami, L. Davidovic, N. Flamand, M. Arita, G. Lambeau, A. Droit, E. Boilard <br> JCI Insight, <https://doi.org/10.1172/jci.insight.152638>

-   *Interpretation of network-based integration from multi-omics longitudinal data*\
    [**A. Bodein**]{.underline}, M.P. Scott-Boyer, O. Perin, K-A. Lê Cao, A. Droit <br> Nucleic Acids Research, <https://doi.org/10.1093/nar/gkab1200>

-   *timeOmics: an R package for longitudinal multi-omics data integration*\
    [**A. Bodein**]{.underline}, M.P. Scott-Boyer, O. Perin, K-A. Lê Cao, A. Droit <br> Bioinformatics, <https://doi.org/10.1093/bioinformatics/btab664>

#### 2021

-   *Integration strategies of multi-omics data for machine learning analysis*\
    M. Picard, M.P. Scott-Boyer, [**A. Bodein**]{.underline}, O. Perin, A. Droit <br> Computational and Structural Biotechnology Journal, <https://doi.org/10.1016/j.csbj.2021.06.030>

#### 2020

-   *Adipose tissue transcriptome is related to pollutant exposure in polar bear mother-cub pairs from Svalbard, Norway*\
    P. Herst, J. Aars, C. Joly-Beauparlant, [**A. Bodein**]{.underline}, M. Dalvai, D. Gagne, A. Droit, J. Bailey, H. Routti <br> Environmental Science & Technology, <https://doi.org/10.1021/acs.est.0c01920>

#### 2019

-   *A generic multivariate framework for the integration of microbiome longitudinal studies with other data types*\
    [**A. Bodein**]{.underline}, O. Chapleur, A. Droit, K-A. Lê Cao <br> Frontiers in Genetics, <https://doi.org/10.3389/fgene.2019.00963>

:::

::: pkg-section

### R Packages

-   netOmics [*2021*]{.cvdate}\
    [**A. Bodein**]{.underline} , M.P. Scott-Boyer, O. Perin, K-A. Lê Cao, A. Droit\
    BioConductor (2021) [doi.org/10.18129/B9.bioc.netOmics](https://doi.org/10.18129/B9.bioc.netOmics)

-   timeOmics [*2019*]{.cvdate}\
    [**A. Bodein**]{.underline} , O. Chapleur, A. Droit, K-A. Lê Cao BioConductor (2019) [doi.org/10.18129/B9.bioc.timeOmics](https://doi.org/10.18129/B9.bioc.timeOmics)

:::

---

::: conf-section

### Talks

-   Integration of Microbiome and Multi-Omics Longitudinal Data <br> [**A. Bodein**]{.underline} , O. Chapleur, A. Droit, K-A. Lê Cao [*2019*]{.cvdate} Presented to : 3\textsuperscript{rd} Workshop in Statistical Algorithms Challenges in Microbiome Data Analysis, New-York, USA

---

### Posters

-   *Informatique quantique pour l'analyse des réseaux biologiques : fondements, algorithmes pour la prédiction de la toxicité* [*Mar. 2026*]{.cvdate}\
    V. Bransolle, [**A. Bodein**]{.underline}, A. Mathieu, A. Droit\
    *Presented to : Journée de l'Axe Endo-néphrologie, Québec, Canada*

-   *Prediction of Drug-Induced Liver Toxicity through Topological Motif Analysis in Protein Networks* [*May 2025*]{.cvdate} D. Benyakhlaf, [**A. Bodein**]{.underline}, A. Droit\
    *Presented to : Journées de la Recherche du CHU de Québec, Québec, Canada*

-   *Amélioration du repositionnement de médicaments avec l'étiquetage de données négatives grâce aux grands modèles de langage* [*Mar. 2025*]{.cvdate}\
    M. Picard, M. Leclercq, [**A. Bodein**]{.underline}, M.P. Scott-Boyer, O. Perin, A. Droit\
    *Presented to : Journée de l'Axe Endo-néphrologie, Québec, Canada*

-   *Tissue-specific network analysis to predict the hepatotoxicity of compounds* [*Aug. 2023*]{.cvdate}\
    M.P. Scott-Boyer, [**A. Bodein**]{.underline}, R. Grall, B. Ambroise, A. Riu, O. Perin, A. Droit\
    *Presented to : 12^th^ World Congress on Alternatives and Animal Use in the Life Sciences, Niagara Falls, Canada*

-   *A framework to integrate multi-omics longitudinal dataset* [*Sept. 2019*]{.cvdate}\
    M.P. Scott-Boyer, [**A. Bodein**]{.underline}, K-A. Lê Cao, O. Perin, A. Droit\
    *Presented to : EMBO\|EMBL - Multiomics to Mechanisms – Challenges in Data Integration, Heidelberg, Germany*

-   *Integration of Microbiome and Multi-Omics Longitudinal Data* [*May 2019*]{.cvdate}\
    [**A. Bodein**]{.underline}, O. Chapleur, A. Droit, K-A. Lê Cao\
    *Presented to : Journées de la Recherche du CHU de Québec, Québec, Canada*

-   *WHORMSS® : Taxonomic and functional exploration from metagenome shotgun sequencing* [*July 2017*]{.cvdate}\
    Y. Laurent, J. Denonfoux, [**A. Bodein**]{.underline}, S. Ferreira\
    *Presented to : Journées Ouvertes en Biologie, Informatique et Mathématiques (JOBIM), Lille, France*

:::
